\section{Introduction}

	The information and communication techonologies expasion has given the population a better access with eletronic devices as celphones, computers and video-games consoles~\cite{tics}. This devices are controlled by the so-called software which gives the gadget funcionalities based on it hardware. Is estimated that in $2019$ the amount of money allocated with software will be about $201$ billion of dollars, justifying the importance and utilization of this sector~\cite{tendencies}.

	With the growth of the software industry the necessity of guarantee the quality of the products to the final users was created, and this necessity was not limited to the huge companies, but also to the small companies, that work on simpler software. The cost of failures in programs are estimated in $1.1$ trillion of dollars in $2016$~\cite{failures}, which could be avoided investing on software testing.

	Based on the presented facts, researchers and companies develop and apply different software test methods. Between these methods are present: Testing Based on Models, Functional Testing, Integration Test, Regression Test, and others that can be applied on the most diverses steps of the software developing proccess, however, with the same objective~\cite{paiva2016aplicaccao}.

	One of the approachs present on the literature to ensure software quality is the so-called Property-Based Testing (PBT). PBT take the principles and expectations in relation to the code behavior and uses it to test the software, this way, specific examples are not applied to test~\cite{fink1997property}. In other words, the main objective is to construct test cases that reveal the presence of failures that are not exposed by a simple code execution.


	Due this facts, in this study, we aim to give an overview about Property-Based Testing making a investigation on the main researchs accomplished on the theme. We are motivated by the currently few studies found on the literature, to the best of our knowledge. This way, we apply in our methodology a systematic mapping technique. Systematic mapping is a searching method that aim to measure the extension of a theme on the literature \cite{petersen2008systematic}, been the best tool to investigate the works on a field. In sum, the main contribution of this paper is A systematic mapping on Property-Based Testing. %% follow up